%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic \& Technical Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % THESIS — TOP for AIOps/Telco audience
  \cventry
    {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {A Closed-Loop Automated Operation Framework for E2E Network Slicing (M.S. Thesis)} % Project title
    {} % Location
    {Oct. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Designing a \textbf{closed-loop AIOps framework} for automated fault detection and assisted remediation in cloud-native O-RAN E2E network slicing environments.}
        \item {Built a \textbf{multi-modal observability platform} unifying logs, metrics, and traces across O-Cloud clusters, eliminating data silos and enabling cross-layer fault localization.}
        \item {Developed an \textbf{automated fault detection pipeline} to identify anomalies across the O-RAN service chain, replacing manual operator analysis to reduce MTTD.}
        \item {Implemented \textbf{safety-first assisted remediation} with human-in-the-loop guardrails, preventing cascading failures during automated recovery operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {\href{https://github.com/ChesterChuTw/winfra-cluster-management}
    {\faGithub\ Infrastructure Automation \& Management for Laboratory Environment}}
    {\href{https://github.com/ChesterChuTw/winfra-cluster-management}{\faGithub\ source code}} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Independently migrated a Kubernetes platform from \textbf{Kubespray + Terraform} to an immutable, GitOps architecture using \textbf{Talos Linux} and \textbf{Flux CD}, including cluster bootstrap, node lifecycle automation, and PV-level data migration.}
        \item {Integrated \textbf{Velero}, \textbf{MinIO}, \textbf{Grafana stack}, \textbf{Keycloak}, and others for backup, storage, access control, and observability.}
        \item {Managed \textbf{Harvester} clusters and migrated to \textbf{Proxmox VE} for improved stability and flexibility.}
        \item {Executed multi-application, multi-version upgrades involving rollbackable database upgrades and data migrations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Teaching Assistant, CSIT, NYCU} % Job title
    {Kubernetes Networking and Security Enhancement for Department Infrastructure} % Project title
    {} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Migrated networking from \textbf{Flannel} to \textbf{Calico} for fine-grained \textbf{NetworkPolicy} enforcement, enabling micro-segmentation aligned with zero-trust principles.}
        \item {Implemented \textbf{Istio Egress Gateway} for unified, auditable outbound traffic management.}
        \item {Evaluated \textbf{External Secrets Operator (ESO)} and \textbf{OpenBao (Vault fork)} for Kubernetes secret management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Multi-Cluster Management System} % Project title
    {} % Location
    {Sep. 2023 -- Jan. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Studied the architecture of a Kubernetes-based \textbf{multi-cluster management system} integrating \textbf{Karmada}, \textbf{Cilium}, and \textbf{Thanos} for cross-cluster orchestration and federated observability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Assistant, Information Technology Service Center, NYCU} % Job title
    {Kubernetes Infrastructure and DevOps Workflow Development} % Project title
    {} % Location
    {Sep. 2023 -- Aug. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Built scalable \textbf{Kubernetes} infrastructure for institutional systems.}
        \item {Enhanced CI/CD automation using \textbf{GitLab CI} to improve delivery reliability.}
      \end{cvitems}
    }

\end{cventries}
