%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic \& Technical Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%	Dev version: Dev-relevant entries first; research/pure-infra entries moved to end.
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {System Administrator, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {\href{https://github.com/ChesterChuTw/winfra-cluster-management}
    {\faGithub\ Infrastructure Automation \& Management for Laboratory Environment}}
    {\href{https://github.com/ChesterChuTw/winfra-cluster-management}{\faGithub\ source code}} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Independently migrated a Kubernetes platform from \textbf{Kubespray + Terraform} to an immutable, GitOps architecture using \textbf{Talos Linux} and \textbf{Flux CD}, including cluster bootstrap, node lifecycle automation, and PV-level data migration.}
        \item {Executed multi-application, multi-version upgrades involving rollbackable database upgrades and data migrations.}
        \item {Integrated \textbf{Velero}, \textbf{MinIO}, \textbf{Grafana stack}, \textbf{Keycloak}, and others for backup, storage, access control, and so on.}
        \item {Managed \textbf{Harvester} clusters and migrated to \textbf{Proxmox VE} for improved stability and flexibility.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Consultant, Koi Studio Ltd.} % Job title
    {System Architecture Planning and Azure Infrastructure Consultation} % Project title
    {} % Location
    {Dec. 2023 -- Nov. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Advised on system architecture and \textbf{Azure} infrastructure design for a software product company.}
        \item {Resolved deployment and integration issues between cloud services and external vendor APIs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Assistant, Information Technology Service Center, NYCU} % Job title
    {Kubernetes Infrastructure and DevOps Workflow Development} % Project title
    {} % Location
    {Sep. 2023 -- Aug. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Built \textbf{Kubernetes} infrastructure for institutional systems and enhanced \textbf{GitLab CI} pipelines to improve delivery reliability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Teaching Assistant, CSIT, NYCU} % Job title
    {Kubernetes Networking and Security Enhancement for Department Infrastructure} % Project title
    {} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Migrated networking from \textbf{Flannel} to \textbf{Calico} for fine-grained \textbf{NetworkPolicy} enforcement.}
        \item {Implemented \textbf{Istio Egress Gateway} for unified outbound traffic management.}
        \item {Evaluated \textbf{External Secrets Operator (ESO)} and \textbf{OpenBao (Vault fork)} for Kubernetes secret management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Multi-Cluster Management System} % Project title
    {} % Location
    {Sep. 2023 -- Jan. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {\textbf{Multi‑cluster management system} integrating \textbf{Karmada}, \textbf{Cilium}, and \textbf{Thanos} for orchestration and observability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {A Closed-Loop Automated Operation Framework for E2E NS (M.S. Thesis)} % Project title
    {} % Location
    {Feb. 2026 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Non-invasive traces and RED metrics generation via \textbf{eBPF}, without NF code changes.}
        \item {\textbf{OTel}-based logs, metrics, and traces collection and cross-modal correlation across O-Cloud clusters.}
        \item {Automated anomaly detection with \textbf{AI-agent-assisted RCA} to reduce MTTD.}
        \item {Safety-first assisted remediation via \textbf{MCP Tool Server} to reduce MTTR.}
      \end{cvitems}
    }

\end{cventries}
