
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%	Dev version: Next.js framework bullet elevated; full-stack delivery language strengthened.
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {R\&D Engineer, R\&D Department} % Job title
    {ISCOM Online International Information Inc.} % Organization
    {Taichung, Taiwan} % Location
    {Jul. 2022 -- Aug. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Established a unified frontend framework with \textbf{Next.js}, adopted across multiple internal products to improve development consistency and code reuse.}
        \item {Designed and implemented internal \textbf{GitLab CI/CD pipelines} to automate build, test, and deployment workflows.}
        \item {Built and operated production \textbf{Kubernetes} clusters across on-premises and cloud environments (\textbf{AKS}).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Engineer / Technical Project Manager, Business Unit} % Job title
    {} % Organization
    {} % Location
    {Jul. 2018 -- Jun. 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Architected and delivered over \textbf{45 web and enterprise projects} end-to-end, spanning e-commerce platforms, POS systems, and GIS-based applications.}
        \item {Built full-stack solutions with \textbf{ASP.NET Core}, \textbf{Laravel}, \textbf{Next.js}, and \textbf{Vue.js}, backed by \textbf{MSSQL} and \textbf{MySQL} databases.}
        \item {Integrated complex third-party services including \textbf{payment gateways}, \textbf{LINE Official Account}, and \textbf{POS hardware APIs}.}
        \item {Modernized legacy \textbf{.NET Framework} codebase to cross-platform, containerizable \textbf{.NET Core} architecture.}
        \item {Supported clients on \textbf{Azure Cloud} deployment, including Web Apps, VMs, and managed databases.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Internship} % Organization
    {Taichung, Taiwan} % Location
    {Jul. 2015 -- Jun. 2018} % Date(s)
    {
      \begin{cvitems}
        \item {\textbf{ISCOM Inc. (2017--2018):} Developed \textbf{ASP.NET MVC} Web APIs integrating public transport data and mapping services.}
        \item {\textbf{BitCloud Co. (2016--2017):} Built responsive UI components and optimized client-side performance for web applications.}
        \item {\textbf{RCE Power Inc. (2015--2016):} Built \textbf{Python Selenium} crawlers with \textbf{MySQL} to automate internal data collection workflows.}
      \end{cvitems}
    }

\end{cventries}
