%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic \& Technical Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    
  \cventry
  {System Administrator, Wireless \& Internet Lab (WinLab), NYCU} % Job title
  {Infrastructure Automation and Management for Laboratory Environment} % Project title
  {} % Location
  {Jul. 2024 -- Present} % Date(s)
  {
    \begin{cvitems}
      \item {Automated cluster provisioning and application deployment via \textbf{Talos Linux} and \textbf{Flux CD}.}
      \item {Integrated \textbf{Velero}, \textbf{MinIO}, \textbf{Grafana}, \textbf{Keycloak}, and others for backup, storage, access control, and other features.}
      \item {Managed \textbf{Harvester} clusters and migrated to \textbf{Proxmox VE} for improved stability and flexibility.}
    \end{cvitems}
  }
  \cventry
  {System Teach Assistant, CSIT, NYCU} % Job title
  {Kubernetes Networking and Security Enhancement for Department Infrastructure} % Project title
  {} % Location
  {Jul. 2024 -- Present} % Date(s)
  {
    \begin{cvitems}
      \item {Migrated networking from \textbf{Flannel} to \textbf{Calico} for fine-grained \textbf{NetworkPolicy} enforcement.}
      \item { Implemented \textbf{Istio Egress Gateway} for unified outbound traffic management.}
      \item {Evaluated \textbf{External Secrets Operator (ESO)} and \textbf{OpenBao (Vault fork)} for Kubernetes secret management.}
    \end{cvitems}
  }
  \cventry
    {Graduate Student Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Observability, Automated Fault Detection and Recovery in Cloud-Native O-RAN Systems (M.S. Thesis)} % Project title
    {} % Location
    {Oct. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Currently contributing to the development of an integrated observability platform that unifies logs, metrics, and traces
across O‑Cloud clusters to enhance real‑time visibility, fault diagnosis and fault recovery.}
      \end{cvitems}
    }
  
  \cventry
  {Technical Consultant, Koi Studio} % Job title
  {System Architecture Planning and Azure Infrastructure Consultation} % Project title
  {} % Location
  {Dec. 2023 -- Nov. 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Assisted in system architecture planning and infrastructure design.}
      \item {Resolved issues related to \textbf{Azure} platform deployment and infrastructure management.}
      \item {Supported integration and troubleshooting between external vendor services.}
    \end{cvitems}
  }

  \cventry
  {Technical Assistant, Information Technology Service Center, NYCU} % Job title
  {Kubernetes Infrastructure and DevOps Workflow Development} % Project title
  {} % Location
  {Sep. 2023 -- Aug. 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Built scalable \textbf{Kubernetes} infrastructure for institutional systems.}
      \item {Enhanced CI/CD automation using \textbf{GitLab CI} to improve delivery reliability.}
    \end{cvitems}
  }

  
  \cventry
    {Graduate Student Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Multi-Cluster Management System} % Project title
    {} % Location
    {Sep. 2023 -- Jan. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Studied the architecture and orchestration of a Kubernetes‑based \textbf{multi‑cluster management system} integrating
\textbf{Karmada}, \textbf{Cilium}, and \textbf{Thanos} for orchestration and observability.}
      \end{cvitems}
    }




    
  % \cventry
  %   {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
  %   {Intent-Based MANO Framework for O-RAN Network Slicing} % Project title
  %   {} % Location
  %   {Apr. 2025 -- Oct. 2025} % Date(s)
  %   {
  %     \begin{cvitems}
  %       \item {Supported the presentation and visualization of the O-RAN-compliant intent-based MANO framework, originally proposed by senior lab members, at \textit{BIOTC 2025} (oral) and \textit{IIHMSP 2025} (poster).}
  %     \end{cvitems}
  %   }
 
\end{cventries}
