%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Observability and AIOps for Cloud-Native O-RAN Systems (M.S. Thesis)} % Project title
    {} % Location
    {Oct. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Currently contributing to the development of an integrated observability platform that unifies logs, metrics, and traces across O-Cloud clusters to enhance real-time visibility, fault diagnosis and fault recovery.} 
      \end{cvitems}
    }
  \cventry
  {System Administrator, Wireless \& Internet Lab (WinLab), NYCU} % Job title
  {Infrastructure Automation and Management for Laboratory Environment} % Project title
  {} % Location
  {Jul. 2024 -- Present} % Date(s)
  {
    \begin{cvitems}
      \item {Implemented \textbf{Infrastructure-as-Code (IaC)} automation using \textbf{Talos Linux} for cluster provisioning and \textbf{Flux CD} for continuous deployment and configuration management across laboratory infrastructure.}
      \item {Integrated and maintained multiple open-source components—including \textbf{Velero}, \textbf{MinIO}, \textbf{Grafana}, \textbf{Keycloak}, and others—to support disaster recovery, storage, observability, and access control across the laboratory infrastructure.}
      \item {Maintained the \textbf{Harvester cluster} used as virtualized workstations and managing compute and storage resources across laboratory nodes.}
      \item {Migrated the Harvester environment to \textbf{Proxmox VE (PVE)} to streamline maintenance, increase stability, and improve resource flexibility.}
    \end{cvitems}
  }
  \cventry
  {System Teaching Assistant, CSIT, NYCU} % Job title
  {Kubernetes Networking and Security Enhancement for Department Infrastructure} % Project title
  {} % Location
  {Jul. 2024 -- Present} % Date(s)
  {
    \begin{cvitems}
      \item {Migrated the clusters networking from \textbf{Flannel} to \textbf{Calico}, enabling fine-grained \textbf{NetworkPolicy} enforcement.}
      \item { Evaluated and implemented an \textbf{Istio Egress Gateway} to centralize outbound traffic routing, facilitating unified traffic management and external access control under Calico.}
      \item {Surveyed and evaluated \textbf{Kubernetes Secret Management} solutions, focusing on \textbf{OpenBao (HashiCorp Vault community fork)} integration.}
    \end{cvitems}
  }

  \cventry
  {Graduate Research Assistant, Information Technology Service Center, NYCU} % Job title
  {Kubernetes Infrastructure and DevOps Workflow Development} % Project title
  {} % Location
  {Sep. 2023 -- Aug. 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Built and maintained the \textbf{Kubernetes-based infrastructure} for institutional systems, enabling scalable and containerized deployment environments.}
      \item {Developed and optimized \textbf{DevOps workflows} leveraging \textbf{GitLab-CI} to enhance automation, reliability, and consistency in system delivery.}
    \end{cvitems}
  }

  
  \cventry
    {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Multi-Cluster Management System (Industry-Academia Collaboration)} % Project title
    {} % Location
    {Sep. 2023 -- Jan. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Studied the architecture and orchestration of a Kubernetes-based \textbf{multi-cluster management system} integrating \textbf{Karmada}, \textbf{Cilium}, and \textbf{Thanos} for orchestration and observability.}
      \end{cvitems}
    }

    
  \cventry
    {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Intent-Based MANO Framework for O-RAN Network Slicing} % Project title
    {} % Location
    {Apr. 2025 -- Oct. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Supported the presentation and visualization of the O-RAN-compliant intent-based MANO framework, originally proposed by senior lab members, at \textit{BIOTC 2025} (oral) and \textit{IIHMSP 2025} (poster).}
      \end{cvitems}
    }
 
\end{cventries}
