
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {R\&D Engineer, R\&D Department} % Job title
    {ISCOM Online International Information Inc. (采威國際資訊股份有限公司)} % Organization
    {Taichung, Taiwan} % Location
    {Jul. 2022 -- Aug. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Deployed and managed \textbf{Kubernetes} across both on-premises and cloud environments (\textbf{Azure Kubernetes Service, AKS}), enabling scalable and portable containerized workloads.}
        \item {Designed and implemented internal \textbf{GitLab CI/CD pipelines} to automate build, test, and deployment workflows, improving development efficiency and release consistency.}
        \item {Established the company's frontend framework foundation using \textbf{Next.js}, providing a unified architecture that simplified development and enabled cross-project code reuse.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Engineer / Technical Project Manager, Business Unit} % Job title
    {ISCOM Online International Information Inc. (采威國際資訊股份有限公司)} % Organization
    {Taichung, Taiwan} % Location
    {Jul. 2018 -- Jun. 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Participated in the development of over \textbf{45 web and enterprise projects}, covering diverse system types such as \textbf{e-commerce platforms}, \textbf{LINE Bot services}, \textbf{POS management systems}, and \textbf{GIS-based information systems}, in collaboration with cross-functional teams.}
        \item {Designed and implemented both frontend and backend systems using diverse frameworks and technologies, including \textbf{ASP.NET Framework}, \textbf{ASP.NET Core}, \textbf{Laravel (PHP)}, \textbf{Vue.js}, and \textbf{Next.js}.}
        \item {Integrated multiple third-party and enterprise services such as \textbf{payment gateways}, \textbf{LINE OA}, and \textbf{POS systems}.}
        \item {Assisted clients in deploying and maintaining applications on the \textbf{Azure Cloud Platform}, managing web apps, virtual machines, and SQL databases for production environments.}
        \item {Led the refactoring of the company's legacy \textbf{.NET Framework} backend foundation into a cross-platform \textbf{.NET Core} architecture, enabling \textbf{containerization} and improving maintainability, deployment flexibility, and cross-project code reuse.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Internship -- ISCOM Online International Information Inc., BitCloud Co., Ltd., and RCE Power Inc.} % Organization
    {Taichung, Taiwan} % Location
    {Jul. 2015 -- Jun. 2018} % Date(s)
    {
      \begin{cvitems}
        \item {(2017–2018) \textbf{ISCOM Online International Information Inc. (采威國際資訊股份有限公司)}: assisted in developing \textbf{ASP.NET MVC} and Web API modules, integrating external data sources such as public transport and mapping APIs, and contributing to enterprise web system development.}
        \item {(2016–2017) \textbf{BitCloud Co., Ltd. (比特雲科訊有限公司)}: supported UI and client-side optimization efforts for commercial web applications, focusing on cross-platform compatibility.}
        \item {(2015–2016) \textbf{RCE Power Inc. (低碳動能開發股份有限公司)}: developed automated data crawlers using \textbf{Python Selenium} and \textbf{MySQL}, streamlining data collection workflows for internal analytics.}
      \end{cvitems}
    }
\end{cventries}


