%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic \& Technical Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%	Google System Lab Engineer version:
%	- Kubernetes Networking elevated to top (recruiter focus)
%	- Fleet management, data collection/visualization angles emphasized
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % NETWORKING — TOP for Google System Lab (recruiter asked networking)
  \cventry
    {System Teaching Assistant, CSIT, NYCU} % Job title
    {Kubernetes Networking and Security Enhancement for Department Infrastructure} % Project title
    {} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Designed and executed a \textbf{network topology migration} from \textbf{Flannel} to \textbf{Calico}, enforcing fine-grained \textbf{NetworkPolicy} for traffic isolation across cluster nodes.}
        \item {Deployed \textbf{Istio Egress Gateway} to centralize and control outbound traffic routing, enabling unified policy enforcement and auditability.}
        \item {Evaluated \textbf{External Secrets Operator (ESO)} and \textbf{OpenBao (Vault fork)} for cluster-wide secrets management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {\href{https://github.com/ChesterChuTw/winfra-cluster-management}
    {\faGithub\ Infrastructure Automation \& Management for Laboratory Environment}}
    {\href{https://github.com/ChesterChuTw/winfra-cluster-management}{\faGithub\ source code}} % Location
    {Jul. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Independently migrated a Kubernetes platform from \textbf{Kubespray + Terraform} to an immutable, GitOps architecture using \textbf{Talos Linux} and \textbf{Flux CD}, including cluster bootstrap, node lifecycle automation, and PV-level data migration.}
        \item {Executed multi-application, multi-version upgrades involving rollbackable database upgrades and data migrations.}
        \item {Deployed \textbf{Grafana stack} (Prometheus, Loki, Grafana) for data collection, analysis, and visualization across the lab infrastructure.}
        \item {Managed \textbf{Harvester} clusters and migrated to \textbf{Proxmox VE} for improved stability and flexibility.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {A Closed-Loop Automated Operation Framework for E2E NS (M.S. Thesis)} % Project title
    {} % Location
    {Feb. 2026 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Non-invasive traces and RED metrics generation via \textbf{eBPF}, without NF code changes.}
        \item {\textbf{OTel}-based logs, metrics, and traces collection and cross-modal correlation across O-Cloud clusters.}
        \item {Automated anomaly detection with \textbf{AI-agent-assisted RCA} to reduce MTTD.}
        \item {Safety-first assisted remediation via \textbf{MCP Tool Server} to reduce MTTR.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Consultant, Koi Studio Ltd.} % Job title
    {System Architecture Planning and Azure Infrastructure Consultation} % Project title
    {} % Location
    {Dec. 2023 -- Nov. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Assisted in system architecture planning and infrastructure design.}
        \item {Resolved issues related to \textbf{Azure} platform deployment and infrastructure management.}
        \item {Supported integration and troubleshooting between external vendor services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Assistant, Information Technology Service Center, NYCU} % Job title
    {Kubernetes Infrastructure and DevOps Workflow Development} % Project title
    {} % Location
    {Sep. 2023 -- Aug. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Built scalable \textbf{Kubernetes} infrastructure for institutional systems.}
        \item {Enhanced CI/CD automation using \textbf{GitLab CI} to improve delivery reliability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student Assistant, Wireless \& Internet Lab (WinLab), NYCU} % Job title
    {Multi-Cluster Management System} % Project title
    {} % Location
    {Sep. 2023 -- Jan. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {\textbf{Multi‑cluster management system} integrating \textbf{Karmada}, \textbf{Cilium}, and \textbf{Thanos} for orchestration and observability.}
      \end{cvitems}
    }

\end{cventries}
